master thesis

### 2018-03-06 Paper - Latex/Paper - Skizze - v3.tex
Paper - move properties of OTL tree to the appendix

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Distribution of Taxa}
        - In our tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
        - The most of them are hardly represented. The major taxonomic groups are: ... \\
        - Here you can see some characteristics of the Multifurcation of the tree. \\
        \begin{figure}[h!]
          \centering
          \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
          \caption{Distribution of Nodes in Rank-Cathegories}
          \label{fig:taxaTable2}
        \end{figure}
        In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
          be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
          taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
          multipliers for some are much bigger and for others much smaller, which you can see in in figure 
          \ref{fig:taxaTable2}. \\
        Please see the appendix on page \pageref{sec:taxaTable2} for a complete table \ref{sec:taxaTable2} 
          of these data. \\
        \todo{Was hierzu ist richtig und wichtig?}

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Distribution of data in the taxa}
        Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
          zugeteilt. \\
        Please see the appendix on page \pageref{sec:taxaTable1} for a complete table \ref{sec:taxaTable1} 
          of these data. \\
        \todo{gibt es einen Zusammenhang zwischen Anzahl} \\
        \todo{max max height zu anzahl nodes in phylum plotten? oder mean max height oder ... 
          (mean, min height...)} \\
        \todo{depth...}

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Taxa}
      The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
        according to recent findings, this is not complete and we lack some taxa in every rank. For 
        example, Hans says that one distinguishes between seven and nine kingdoms 
        \cite{CavalierSmith1981}. \\
      In section \pageref{sec:listPhyla} of the appendix you can find a list of all phyla.

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Appendices}
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{List of all phyla}\label{sec:listPhyla}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Distribution of data in the taxa}\label{sec:taxaTable1}
    \begin{center}
      \begin{tabular}{ |l|r|l|r|r| }
        \hline
        Kingdom (3) & Number of Nodes & Phylum (25) & Number of Nodes & max max height \\
        \hline \hline
        Metazoa & 1 465 207 & Arthropoda & 1 170 539 & 54 \\
        & & Chordata & 106 650 & 74 \\
        & & Mollusca & 80 022 & 22 \\
        & & Platyhelminthes & 27 141 & 9 \\
        & & Nematoda & 24 564 & 23 \\
        & & Cnidaria & 14 878 & 36 \\
        & & Porifera & 11 737 & 26 \\
        & & Echinodermata & 10 654 & 14 \\
        & & Bryozoa & 8 631 & 11 \\
        & & Rotifera & 3 093 & 7 \\
        & & Nemertea & 1 793 & 7 \\
        & & Tardigrada & 1 654 & 7 \\
        & & Acanthocephala & 1 596 & 6 \\
        & & Brachiopoda & 1 055 & 9 \\
        & & Nematomorpha & 633 & 7 \\
        & & Chaetognatha & 360 & 7 \\
        & & Hemichordata & 196 & 5 \\ 
        & & Cycliophora & 11 & 5 \\ 
        % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0          \hline
        Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
        & & Basidiomycota & 92 931 & 18 \\
        & & Microsporidia & 1 949 & 6 \\ 
        & & Glomeromycota & 1 490 & 6 \\
        & & Chytridiomycota & 1 456 & 6 \\
        % 254871-157045-92931-1949-1490-1456 = 0
        \hline
        Chloroplastida & 121 239 & Streptophyta & 120 731 & 49 \\
        & & Chlorophyta & 508 & 6 \\
        % 121239-120731-508 = 0
        \hline  
      \end{tabular}
    \end{center}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Taxa table}\label{sec:taxaTable2}
    \begin{center}
      % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
      \begin{tabular}{ |l|r||r|r|r| }
        \hline
        Taxa & Number of Nodes & Internal Nodes & Leaf Nodes & Terminal Leaf Nodes \\
        \hline \hline
        \setrow{\bfseries}domain & 1 & 1 & &  \\ \hline
        \setrow{\bfseries}kingdom & 3 & 3 & &  \\
        subkingdom & 2 & 2 & & \\
        infrakingdom & 5 & 5 & & \\
        superphylum & 2 & 2 & & \\ \hline
        \setrow{\bfseries}phylum & 57 & 54 & 3 & \\
        subphylum & 22 & 20 & 2 & \\
        infraphylum & 2 & 2 & & \\
        superclass & 8 & 8 & & \\ \hline
        \setrow{\bfseries}class & 209 & 175 & 34 & \\
        subclass & 120 & 106 & 14 & \\
        infraclass & 14 & 11 & 3 & \\
        superorder & 40 & 37 & 3 & \\ \hline
        \setrow{\bfseries}order & 1014 & 772 & 242 & \\
        suborder & 285 & 222 & 63 & \\
        infraorder & 95 & 78 & 17 & \\
        parvorder & 14 & 12 & 2 & \\
        superfamily & 829 & 626 & 203 & \\ \hline
        \setrow{\bfseries}family & 8449 & 6143 & 2306 & \\
        subfamily & 3090 & 2250 & 840 & \\
        supertribe & 1 & 0 & 1 & \\
        tribe & 1764 & 1285 & 479 & \\
        subtribe & 435 & 359 & 77 & \\ \hline
        \setrow{\bfseries}genus & 164656 & 105452 & 59204 & \\
        subgenus & 1266 & 869 & 397 & \\
        section & 3 & 2 & 1 & \\
        subsection & 1 & 1 & 0 & \\
        species group & 365 & 288 & 77 & \\
        species subgroup & 123 & 100 & 23 & \\ \hline
        \setrow{\bfseries}species & 2247251 & 7423 & 2239828 & 2228993 \\
        subspecies & 22437 & 75 & 22362 & 22239 \\
        variety & 1755 & 7 & 1748 & 1726 \\
        varietas & 5970 & 19 & 5951 & 5909 \\
        forma & 1181 & & 1181 & 1181 \\
        \hline \hline
        no rank & 954 & 719 & 235 & 7 \\
        no rank - terminal & 37452 & & 37452 & 37452 \\
        (no entry) & 40099 & 40099 & & \\
        \hline  
      \end{tabular}
    \end{center}
    extended leaf nodes (real leaf nodes)

>>>>

      We took a closer look at some of the features of the Synthesis tree. On the one hand the 
        distribution of the taxa and on the other the distribution of the nodes on the taxa. Since this
        is not directly relevant to our study, there is a section in the appendix \ref{sec:otl analysis}.

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Taxa}
      The investigation of the taxonomy revealed that our tree has three kingdoms: Chloroplastida, 
        Metazoa, Fungi, 53 phyla, 195 classes and 924 orders. \\
      Since the analysis of the tree is not part of this work, it should be mentioned here that, 
        according to recent findings, this is not complete and we lack some taxa in every rank. For 
        example, Hans says that one distinguishes between seven and nine kingdoms 
        \cite{CavalierSmith1981}. \\
      In section \pageref{subsec:listPhyla} of the appendix you can find a list of all phyla.

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Appendices}
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{OTL analysis}\label{sec:otl analysis}

    %---------------------------------------------------------------------------------------------------
    \subsection{List of all phyla}\label{subsec:listPhyla}

@@

    %---------------------------------------------------------------------------------------------------
    \subsubsection{Distribution of Taxa}
    - In the tree we can distinguish 28 different Taxa with the OTL taxonomic tree. \\
    - The most of them are hardly represented. The major taxonomic groups are: ... \\
    - Here you can see some characteristics of the Multifurcation of the tree. \\
    \begin{figure}[h!]
      \centering
      \includegraphics[width=0.9\textwidth]{Figures/TaxaTable2.JPG}
      \caption{Distribution of Nodes in Rank-Cathegories}
      \label{fig:taxaTable2}
    \end{figure}
    In a phylogeny, the taxonomic division of the tree is far too coarse, meaning that there should 
      be more subtaxa or 'unranked' nodes. But the closer we get to the root, the more the pure
      taxonomic tree is reflected. If the tree were binary, the taxa would have to double. But the 
      multipliers for some are much bigger and for others much smaller, which you can see in in figure 
      \ref{fig:taxaTable2}. \\
      ... (see Table \ref{table:...})

    \begin{table}[h!]
      \begin{center}
        % \begin{tabular}{ |>{\rowmac}l|>{\rowmac}r|<{\clearrow} }
        \begin{tabular}{ |l|r||r|r|r| }
          \hline
          Taxa & Number of Nodes & Internal Nodes & Leaf Nodes & Terminal Leaf Nodes \\
          \hline \hline
          \setrow{\bfseries}domain & 1 & 1 & &  \\ \hline
          \setrow{\bfseries}kingdom & 3 & 3 & &  \\
          subkingdom & 2 & 2 & & \\
          infrakingdom & 5 & 5 & & \\
          superphylum & 2 & 2 & & \\ \hline
          \setrow{\bfseries}phylum & 57 & 54 & 3 & \\
          subphylum & 22 & 20 & 2 & \\
          infraphylum & 2 & 2 & & \\
          superclass & 8 & 8 & & \\ \hline
          \setrow{\bfseries}class & 209 & 175 & 34 & \\
          subclass & 120 & 106 & 14 & \\
          infraclass & 14 & 11 & 3 & \\
          superorder & 40 & 37 & 3 & \\ \hline
          \setrow{\bfseries}order & 1014 & 772 & 242 & \\
          suborder & 285 & 222 & 63 & \\
          infraorder & 95 & 78 & 17 & \\
          parvorder & 14 & 12 & 2 & \\
          superfamily & 829 & 626 & 203 & \\ \hline
          \setrow{\bfseries}family & 8449 & 6143 & 2306 & \\
          subfamily & 3090 & 2250 & 840 & \\
          supertribe & 1 & 0 & 1 & \\
          tribe & 1764 & 1285 & 479 & \\
          subtribe & 435 & 359 & 77 & \\ \hline
          \setrow{\bfseries}genus & 164656 & 105452 & 59204 & \\
          subgenus & 1266 & 869 & 397 & \\
          section & 3 & 2 & 1 & \\
          subsection & 1 & 1 & 0 & \\
          species group & 365 & 288 & 77 & \\
          species subgroup & 123 & 100 & 23 & \\ \hline
          \setrow{\bfseries}species & 2247251 & 7423 & 2239828 & 2228993 \\
          subspecies & 22437 & 75 & 22362 & 22239 \\
          variety & 1755 & 7 & 1748 & 1726 \\
          varietas & 5970 & 19 & 5951 & 5909 \\
          forma & 1181 & & 1181 & 1181 \\
          \hline \hline
          no rank & 954 & 719 & 235 & 7 \\
          no rank - terminal & 37452 & & 37452 & 37452 \\
          (no entry) & 40099 & 40099 & & \\
          \hline  
        \end{tabular}
        \caption{\todo{...}}
        \label{table:...} 
      \end{center}  
    \end{table}
    extended leaf nodes (real leaf nodes)

  %---------------------------------------------------------------------------------------------------
  \subsubsection{Distribution of data in the taxa}
    Mithilfe des taxonomischen Baums von OTL haben wir die Knoten ihren Kingdoms, Phyla und Classes 
      zugeteilt (see Table \ref{table:...}). \\

    \begin{table}[h]
      \begin{center}
        \begin{tabular}{ |l|r|l|r|r| }
          \hline
          Kingdom (3) & Number of Nodes & Phylum (25) & Number of Nodes & max max height \\
          \hline \hline
          Metazoa & 1 465 207 & Arthropoda & 1 170 539 & 54 \\
          & & Chordata & 106 650 & 74 \\
          & & Mollusca & 80 022 & 22 \\
          & & Platyhelminthes & 27 141 & 9 \\
          & & Nematoda & 24 564 & 23 \\
          & & Cnidaria & 14 878 & 36 \\
          & & Porifera & 11 737 & 26 \\
          & & Echinodermata & 10 654 & 14 \\
          & & Bryozoa & 8 631 & 11 \\
          & & Rotifera & 3 093 & 7 \\
          & & Nemertea & 1 793 & 7 \\
          & & Tardigrada & 1 654 & 7 \\
          & & Acanthocephala & 1 596 & 6 \\
          & & Brachiopoda & 1 055 & 9 \\
          & & Nematomorpha & 633 & 7 \\
          & & Chaetognatha & 360 & 7 \\
          & & Hemichordata & 196 & 5 \\ 
          & & Cycliophora & 11 & 5 \\ 
          % 1465207-(1170539+106650+80022+27141+24564+14878+11737+10654+8631+3093+1793+1654+1596+1055+633+360+196+11) = 0          \hline
          Fungi & 254 871 & Ascomycota & 157 045 & 19 \\ 
          & & Basidiomycota & 92 931 & 18 \\
          & & Microsporidia & 1 949 & 6 \\ 
          & & Glomeromycota & 1 490 & 6 \\
          & & Chytridiomycota & 1 456 & 6 \\
          % 254871-157045-92931-1949-1490-1456 = 0
          \hline
          Chloroplastida & 121 239 & Streptophyta & 120 731 & 49 \\
          & & Chlorophyta & 508 & 6 \\
          % 121239-120731-508 = 0
          \hline  
        \end{tabular}
        \caption{\todo{...}}
        \label{table:...} 
      \end{center}  
    \end{table}
